Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-01-17 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}[]
     \centering
     \includegraphics[width=\columnwidth]{figures/sbc_rank_plot_NPE_C.pdf}
     \includegraphics[width=\columnwidth]{figures/tarp_plot_NPE_C.pdf}
     \vspace{-.5cm}
     \caption{\emph{Left:} SBC ranks of ground truth parameters under the inferred posterior samples for each of the six parameters (red bars). The grey area shows the 99\% confidence interval of a uniform distribution given the number of samples provided. \emph{Right:} }
     \label{fig:sbc}
     \script{evaluate_sbi.py}
\end{figure*}

>>>>

\begin{figure*}[]
     \centering
     \includegraphics[width=\textwidth]{figures/sbc_rank_plot_NPE_C.pdf}
     %\vspace{-.5cm}
     \caption{SBC ranks of ground truth parameters under the inferred posterior samples for each of the six parameters (red bars). The grey area shows the 99\% confidence interval of a uniform distribution given the number of samples provided.}
     \label{fig:sbc}
     \script{evaluate_sbi.py}
\end{figure*}

\begin{figure}[]
     \centering
     \includegraphics[width=\columnwidth]{figures/tarp_plot_NPE_C.pdf}
     %\vspace{-.5cm}
     \caption{TARP plot.}
     \label{fig:sbc}
     \script{evaluate_sbi.py}
\end{figure}
